\documentclass{article}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\geometry{a4paper, total={185mm,257mm}}


\title{Curriculum Vitae}
\author{David Lawton}
\date{20th Jan. 2024}

\begin{document}

\maketitle
\vfill

\section*{Personal Details:}
\hrule~\\
Address: 39 Landscape Park, Churchtown, Dublin 14. D14 A304.\\
Contact Number: +353 83 834 4417\\
Contact Email: davidj.lawton@gmail.com or lawtond@tcd.ie\\

\section*{Education:}
\hrule~\\
Trinity College Dublin, BA Theoretical Physics. Summer 2023 Grade - 1, 70\%. Summer 2024 Grade - Pass at Reassesments, 67\% (Introduction to Group Theory failed on first attempt, 90\% on reassesment.)\\
-Relevant Modules:\\
\indent Computer Simulation I, Physics for Theoretical Physics.\\
All other modules can be found at \url{https://www.maths.tcd.ie/undergraduate/modules/}

\section*{Work Experience:}
\hrule~\\
While I have worked previously in the hospitality industry, and I believe it has given me the ability to function as part of a team, I do not deem it relevant enough to warrant inclusion. 
\section*{Awards/Acknowledgements:}
\hrule~\\
Achieved Bronze Gaisce Award in 2020.  Earned maximum points in LC 2022, including H1's in Maths, Physics, Applied Maths.  Received Entrance Exhibition Scholarship from TCD.  One of eight students in the course being put forward to go to PLANCKS 2025 UK \& Ireland Preliminaries in Swansea, by the TPSA.  Participated in TPSA Hackathon (Data Analysis, Python) and coding workshops (QisKit, MCMC methods) in 2024. Volunteer experience fundraising at the Hope Foundation (2019/20).

\section*{Skills}
\hrule~\\
Software/Tools: Experience in use of Github, as well as proficiency in Latex, Jupyter, and Microsoft Office tools.\\
Programming: Experience in Python and C++, including OOP and parallel programming, as well as computing in a Linux environment. I am also learning Rust currently.
\section*{References:}
\hrule~\\
Dr. Chaolun Wu, Teaching Fellow, School of Maths, Trinity College Dublin. \textbf{wuch@tcd.ie}
\section*{Miscellaneous}
\hrule~\\
$[$Trinity College Dublin$]$ Theoretical Physics Student Association; \textit{Member} (2022-2025)


\end{document}
