\documentclass{article}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{xfrac}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\geometry{a4paper, total={180mm,257mm}, left=15mm, top=5mm}


\title{Curriculum Vitae}
\author{David Lawton}
\date{13th Jan. 2024}

\begin{document}

\maketitle
\vfill

\section*{Personal Details:}
\hrule~\\
Address: 39 Landscape Park, Churchtown, Dublin 14. D14 A304.\\
Contact Number: +353 83 834 4417\\
Contact Email: davidj.lawton@gmail.com or lawtond@tcd.ie\\

\section*{Education:}
\hrule~\\
Trinity College Dublin, BA Theoretical Physics. Summer 2023 Grade - 1, 70\%. Summer 2024 Grade - Pass at Reassesments, 67\% (Introduction to Group Theory failed on first attempt, 90\% on reassesment.)\\
-Relevant Modules:
\begin{itemize}
\item Quantum Mechanics I \& II
\item Advanced Classical Mechanics I \& II
\item Classical Field Theory, Electrodynamics
\item Statistical Mechanics I \& II
\item Condensed Matter I
\item Computer Simulation I
\item Linear PDEs
\end{itemize}
All other modules can be found at \url{https://www.maths.tcd.ie/undergraduate/modules/}

\section*{Work Experience:}
\hrule~\\
No research experience in physics to date. 
\section*{Awards/Acknowledgements:}
\hrule~\\
Achieved Bronze Gaisce Award.  Earned maximum points in LC 2022, including H1's in Maths, Physics, Applied Maths.  Received Entrance Exhibition Scholarship from TCD.  One of eight students in the course being put forward to go to PLANCKS 2025 UK \& Ireland Preliminaries in Swansea, by the TPSA.  Participated in TPSA Hackathon (Data Analysis, Python) and coding workshops (QisKit, MCMC methods) in 2024.

\section*{Skills}
\hrule~\\
Software/Tools: Experience in use of Mathematica, as well as proficiency in Latex, Jupyter\\
Programming: Experience in Python and C++, as well as computing in a Linux environment.
\section*{Miscellaneous}
\hrule~\\
$[$Trinity College Dublin$]$ Theoretical Physics Student Association; \textit{Member} (2022-2025)


\end{document}