
\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{fancyhdr}

% Set the page margins
\geometry{top=1in, bottom=1in, left=1.5in, right=1.5in}

% Set the header and footer
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\renewcommand{\headrulewidth}{0pt} % Remove the header rule line
\rhead{David Lawton}
\cfoot{\thepage}
\signature{David Lawton.}

\begin{document}

\begin{letter}{Joshua Krauß\\
    RPTU Kaiserslautern-Landau\\
    Erwin-Schrödinger Straße 46\\
    67663 Kaiserslautern \\
    Germany}

\opening{Dear Joshua Krauß,}
I am writing to you to apply for the RISE project `\textit{Theory for Photon Bose-Einstein Condensates}' at RPTU Kaiserslautern-Landau. I am a Junior Sophister student at Trinity College Dublin studying Theoretical Physics. Having read the project description, I would be excited to work on the described PBEC vortices and their interactions. I believe that I have the necessary background to contribute to the project, and the prospect of comparisons with empirical data within the project is particularly appealing.\\

As an undergraduate student, I have recently studied, and will in the coming semester study, modules in complex analysis, linear PDEs, quantum mechanics, statistical mechanics and electrodynamics, with a heavy emphasis on the underlying mathematics. I believe many of the topics covered in these courses, as described on the TCD maths website, would allow me to garner a solid understanding of the subjects being researched, as well as providing me the tools to contribute to analytical research. I have found these modules both enjoyable and inspiring, and have no doubt I would feel the same about such exciting research.\\

In addition to the high quality theoretical physics foundation I have outlined, I have also taken a module in computer simulations. I therefore have a decent understanding of many numerical methods, as well as their use in Python, especially as applied to physical and mathematical problems.\\

To conclude, I am applying for this project due to my interest in the photon Bose-Einstein condensates being researched, especially in terms of an analytical description, and the possible experimental comparisons. Thank you for your considerations.\\

\closing{Yours sincerely,}

\end{letter}
\end{document}